The impact of gas bulk rotation on the Lyman-$\alpha$ line

### 2013-09-04 paper/Analisis.tex
one more paragraph full of historical references

The detection of strong \ly emission lines has become an essential
method in extragalactic astronomy to find distant star-forming
galaxies
\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}. The
galaxies detected using this method receive the 
name of \ly emitters (LAEs). A detailed examination of this galaxy
population has diverse implications for galaxy formation, reonization
and the large scale structure of the Universe. Attempts to fully
exploit the physical information included in the \ly line require an
understading of all the physical factor sinvolved in shaping the
line. Due to the resonant nature of this line, these physical factors
include temperature, density and bulk velocity field of the neutral
Hydrogen in the emitting galaxy and its surroundings.

[Line morphology is being measured observationally.]

>>>>

The detection of strong \ly emission lines has become an essential
method in extragalactic astronomy to find distant star-forming
galaxies
\citep{PartridgePeebles,Rhoads00,Gawiser2007,Koehler2007,Ouchi08,Yamada2012,Schenker2012}.
The galaxies detected using this method receive the 
name of \ly emitters (LAEs). A detailed examination of this galaxy
population has diverse implications for galaxy formation, reonization
and the large scale structure of the Universe. Attempts to fully
exploit the physical information included in the \ly line require an
understading of all the physical factors involved in shaping the
line. Due to the resonant nature of this line, these physical factors
include temperature, density and bulk velocity field of the neutral
Hydrogen in the emitting galaxy and its surroundings.

A basic understanding for the quantitative behaviour of the \ly line
has been reached through analytical studies in the case of a static
configurations, such as uniform slabs
\citep{Harrington73,Neufeld90} and  uniform spheres
\citep{Dijkstra06}. Analytical studies of configurations including
some kind of bulk flow only include the case of a sphere with a Hubble
like expansion flow \citep{LoebRybicki}.

A more detailed quantification of the \ly line has been reached using
Monte Carlo simulations \citep{Auer68,Avery68,Adams72}. In the last
two decades these studies have become more popular due to the
availability of computing power. Early into the 21st century the first
studies focused on on homogeneous and static media
\citep{Ahn00,Ahn01,Zheng02}. Later on the effects of clumpy media
\citep{Hansen06} and expanding/contracting shell/spherical geometries started to
be studied \citep{Verhamme06,Dijkstra06}. Similar codes have applied
these results to semi-analytical models of galaxy formation \citep{Orsi12} and
results of large hydrodynamical simulations
\citep{CLARA,Forero-Romero12}. Recently Monte Carlo codes have also
been applied to the results of high resolution hydrodynamical
simulations \citep{Laursen09,Yajima12}.

. In this
context a lot of attention has been paid to effects that might induce
asymmetric line profiles and to the estimation of the escape fraction in the presence of dust.

The bulk gas velocity
plays a central role in the theoretical studies of the \ly line.
